The problem and promise of scale in multilayer networks

### 2020-01-31 paper/manuscript.Rmd
plenty of reflowing

Animal social network analysis is a well-developed tool used to measure the
relationships of individuals and organization of social systems (Krause et al.
2009; Wey et al. 2008; Croft et al. 2008). Social network analysis provides
insight into the structure of social communities and social network properties,
which can influence population dynamics and evolutionary processes
(Pinter-Wollman et al. 2014; Kurvers et al. 2014). Despite the widespread use
and innovation of traditional social network analysis (Webber & Vander Wal
2019), it typically considers a single scale of sociality in a given network
(monolayer), drastically simplifying the potential complexity of animal social
systems (Finn et al. 2019). Unlike traditional monolayer social networks,
multilayer networks explicitly consider social systems across contexts,
including scale-dependent contexts (Pilosof et al. 2017). Multilayer networks
are made up of multiple layers, each representing different classes of
individuals (e.g. male or female), types of behaviours (e.g. grooming,
travelling, or foraging), spatial areas (e.g. local or regional), or temporal
windows (e.g. daily or seasonal) (Kivela et al. 2014; Porter 2018). Multilayer
networks are relatively novel to studies of animal behaviour (Finn et al. 2019;
Silk et al. 2018), although they have been used to describe multidimensional
human social systems, complex transportation networks, and neural networks (Silk
et al. 2018). The role of scale within multilayer social networks remains
unexplored but provides a unique opportunity to develop novel understanding of
variation in the temporal or spatial scales associated with social systems.

@@

* Neighbors/neighborhood (number of unique actors directly connected to each focal)
Neighbors = degree within a network layer
But across a multilayer network with multiple layers, some neighbors are repeated.

@@

### Each metric's interpretation
* Multidegree: sum of degree across layers. High multidegree = connected to many individuals across layers. Low multidegree = not connected to many individuals across layers. 
* Degree deviation: deviation of degree across layers. High degree deviation = large difference between degree for an individual across layers. Low degree deviation = individuals are similarly connected across layers. 
* Graph strength: weighted version of degree. High graph strength = highly connected. Not summed in this case across layers. 
* Neighbors: number of unique individuals adjacent to each actor. Considered in a single layer, this is equal to the degree. 
* Neighborhood: number of unique individuals across all layers. High neighborhood = a high number of unique individuals connected to an actor. 
* Relevance: layer centric metric, corresponding to the number of neighbors on a layer divided by the total neighborhood for each actor. High relevance means that the layer is highly relevant to the individuals connections. A low relevance means this layer does not contribute many neighbors to an individuals overall neighborhood. 
* Connective redundancy: the total multilayer neighborhood divided by the multidegree. High connective redundancy indicates a multilayer network that has many repeated edges across layers between an actor and its neighbours. Low connective redundancy indicates that each layer is important for preserving all social ties. 
* Layer similarily: how similar each layer is (Brodka 2018). Pearson's correlation coefficient of degree vectors for each layer, comparing each landcover across seasons.

@@

  1) How do social phenotypes across scales differently influence fitness? Are some temporal or social scales better predictors for different fitness metrics?

  2) Why do individuals associate more strongly with certain conspecifics in some habitats? What, if any, is the role of movement in the context of habitat networks?

  3) How, and why, does the spatial scale of perception influence, e.g. auditory, visual, or chemotaxis, influence the  social environment across scales? What is the role of memory, and by extension social and spatial cognition, as animals navigate their environment and make decisions about where to move next?

>>>>

Animal social network analysis is a well-developed tool used to measure the
relationships of individuals and organization of social systems (Krause et al.
2009; Wey et al. 2008; Croft et al. 2008). Social network analysis provides
insight into the structure of social communities and social network properties,
which can influence population dynamics and evolutionary processes
(Pinter-Wollman et al. 2014; Kurvers et al. 2014). Despite the widespread use
and innovation of traditional social network analysis (Webber & Vander Wal
2019), it typically considers a single scale of sociality in a given network
(monolayer), drastically simplifying the potential complexity of animal social
systems (Finn et al. 2019).

Unlike traditional monolayer social networks,
multilayer networks explicitly consider social systems across contexts,
including scale-dependent contexts (Pilosof et al. 2017). Multilayer networks
are made up of multiple layers, each representing different classes of
individuals (e.g. male or female), types of behaviours (e.g. grooming,
travelling, or foraging), spatial areas (e.g. local or regional), or temporal
windows (e.g. daily or seasonal) (Kivela et al. 2014; Porter 2018). Multilayer
networks are relatively novel to studies of animal behaviour (Finn et al. 2019;
Silk et al. 2018), although they have been used to describe multidimensional
human social systems, complex transportation networks, and neural networks (Silk
et al. 2018). The role of scale within multilayer social networks remains
unexplored but provides a unique opportunity to develop novel understanding of
variation in the temporal or spatial scales associated with social systems.

@@

* Neighbors/neighborhood (number of unique actors directly connected to each focal)

Neighbors = degree within a network layer
But across a multilayer network with multiple layers, some neighbors are repeated.

@@

### Each metric's interpretation
* Multidegree: sum of degree across layers. High multidegree = connected to many
individuals across layers. Low multidegree = not connected to many individuals
across layers.

* Degree deviation: deviation of degree across layers. High degree deviation =
large difference between degree for an individual across layers. Low degree
deviation = individuals are similarly connected across layers.

* Graph strength: weighted version of degree. High graph strength = highly
connected. Not summed in this case across layers.

* Neighbors: number of unique individuals adjacent to each actor. Considered in
a single layer, this is equal to the degree.

* Neighborhood: number of unique individuals across all layers. High
neighborhood = a high number of unique individuals connected to an actor.

* Relevance: layer centric metric, corresponding to the number of neighbors on a
layer divided by the total neighborhood for each actor. High relevance means
that the layer is highly relevant to the individuals connections. A low
relevance means this layer does not contribute many neighbors to an individuals
overall neighborhood.

* Connective redundancy: the total multilayer neighborhood divided by the
multidegree. High connective redundancy indicates a multilayer network that has
many repeated edges across layers between an actor and its neighbours. Low
connective redundancy indicates that each layer is important for preserving all
social ties.

* Layer similarily: how similar each layer is (Brodka 2018). Pearson's
correlation coefficient of degree vectors for each layer, comparing each
landcover across seasons.

@@

1. How do social phenotypes across scales differently influence fitness? Are
some temporal or social scales better predictors for different fitness metrics?

1. Why do individuals associate more strongly with certain conspecifics in some
habitats? What, if any, is the role of movement in the context of habitat
networks?

1. How, and why, does the spatial scale of perception influence, e.g. auditory,
visual, or chemotaxis, influence the  social environment across scales? What is
the role of memory, and by extension social and spatial cognition, as animals
navigate their environment and make decisions about where to move next?
